### 2016-10-16 propositions.tex
Update propositions

\item Supporting hybrid thread mapping model in object-oriented languages
such as Java is a desirable but currently unrealized feature because of implementation
complexity.

@@

\item The increasing importance of concurrent and distributed programming,
similar to the shift of structured programming to object orientation,
requires more of mentality change rather than languages and tools.

>>>>

\item Supporting a hybrid thread mapping model in object-oriented languages
such as Java is a desirable but currently unrealized feature because of implementation
complexity.

@@

\item The increasing importance of concurrent and distributed programming,
similar to the shift of structured programming to object orientation,
requires more of a mentality change rather than languages and tools.
